archivo de trabajo

### 2021-04-27 final/script.Rmd
Update script.Rmd

1. Badasyan & Silva (2012). International Journal of Education Economics and Development. (Brasil). PSM en año antes y año después de la reforma. standardized Portuguese and mathematics tests that students in all public schools take in the 8th grade. TOT: +, ***
2. Bessone, Dahis, Ho. (2020). The Impact of 3G Mobile Internet on Educational
Outcomes in Brazil. MIT. Two way fixed effects y non parametric diff in diff. 10 años de Brasil (Prova Brasil) que es cada 2 años. en TWFE. El coeficiente es 0. 
3. Malamud, Cueto, Cristia, Beuermann. (2019) Journal of development economics. Peru. We compare children who were randomly chosen to receive laptops with high-speed internet
access to (i) those who did not receive laptops and (ii) those who only received laptops without internet. Regresión en experimento aleatorizado ie Estimador de Neyman=? en digital skills, cognitive skills, y academic skills. Laptop + internet significativos en digital skills, ie XO test (1.00), PC test(.21), Internet test(.33), digital skills index (.53), no en resultados de matemáticas, reading, ni academic achievement index, ni en grades, ni en teachers perceptions (del estudiante).  Resultados en desviaciones estándar. (ATT)
4. Vigdor & Ladd. Economic Inquiry. 2010. North Carolina. Home computer access. estudiantes de 5 y 8, en mate y lectura. Efectos fijos -1% y -1.3% SD en math y reading. 
5. Belo, Ferreira, Felang. 2014. Middle schools de portugal. Broadband in School: Impact on Student Performance. Management science. broadband to schools on students'
performance. Primeras diferencias con efectos fijos. grades reduce 0.78 of a standard deviation,
6. Fairlie, Robinson, 2013.EXPERIMENTAL EVIDENCE ON THE EFFECTS OF HOME COMPUTERS ON
ACADEMIC ACHIEVEMENT AMONG SCHOOLCHILDREN . Home computers. American Economic Journal: Applied Economics. RCT de dar laptops gratis. no correlación con pasar más tiempo en tarea, en entreggar a tiempo

@@

>>>>

1. Badasyan & Silva (2012). International Journal of Education Economics and Development. (Brasil). PSM en año antes y año después de la reforma. standardized Portuguese and mathematics tests that students in all public schools take in the 8th grade. TOT: +, ***
2. Bessone, Dahis, Ho. (2020). The Impact of 3G Mobile Internet on Educational
Outcomes in Brazil. MIT. Two way fixed effects y non parametric diff in diff. 10 años de Brasil (Prova Brasil) que es cada 2 años. en TWFE. El coeficiente es 0. 
3. Malamud, Cueto, Cristia, Beuermann. (2019) Journal of development economics. Peru. We compare children who were randomly chosen to receive laptops with high-speed internet
access to (i) those who did not receive laptops and (ii) those who only received laptops without internet. Regresión en experimento aleatorizado ie Estimador de Neyman=? en digital skills, cognitive skills, y academic skills. Laptop + internet significativos en digital skills, ie XO test (1.00), PC test(.21), Internet test(.33), digital skills index (.53), no en resultados de matemáticas, reading, ni academic achievement index, ni en grades, ni en teachers perceptions (del estudiante).  Resultados en desviaciones estándar. (ATT)
4. Vigdor & Ladd. Economic Inquiry. 2010. North Carolina. Home computer access. estudiantes de 5 y 8, en mate y lectura. Efectos fijos -1% y -1.3% SD en math y reading. 
5. Belo, Ferreira, Felang. 2014. Middle schools de portugal. Broadband in School: Impact on Student Performance. Management science. broadband to schools on students'
performance. Primeras diferencias con efectos fijos. grades reduce 0.78 of a standard deviation,
6. Fairlie, Robinson, 2013.EXPERIMENTAL EVIDENCE ON THE EFFECTS OF HOME COMPUTERS ON
ACADEMIC ACHIEVEMENT AMONG SCHOOLCHILDREN . Home computers. American Economic Journal: Applied Economics. RCT de dar laptops gratis. no correlación con pasar más tiempo en tarea, en entreggar a tiempo
7. Diff in diff con EF y de tiempo. Efecto de fibra en SD de la evaluación nacional. 1% SD en los que estban en la media nacional o arriba de ella. 1.814 SD para niños y 1.26 para niñas

@@

the impact of Internet access on poverty reduction, as determined by our study, reinforces the idea that universalizing access to this service contributes to improving the welfare of a nation’s inhabitants. The results of Internet access in the Mexican population show, with high statistical reliability, that this service is a tool which can help decrease the number of poor people and could therefore become a mechanism to improve the poverty indicators recorded in medium- and low-income countries around the world
